\documentclass[11pt]{report}
\usepackage[scaled]{helvet}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lipsum}
\usepackage{inconsolata}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{setspace}
\renewcommand\familydefault{\sfdefault}
\pagenumbering{gobble}

\begin{document}

\title{Test Plan - Intersect}
\author{James Viner}
\date{} %Remove date
\maketitle

\doublespacing

\pagebreak
\section*{Sample Files}
\subsubsection*{\texttt{\textcolor{red}{american-english.txt}}}
A copy of the american-english dictionary file.
\subsubsection*{\texttt{\textcolor{red}{empty.txt}}}
An empty file
\subsubsection*{\texttt{\textcolor{red}{headphonetic.txt}}}
The first ten lines from phonetic.txt with the last letter capitalized.
\subsubsection*{\texttt{\textcolor{red}{phonetic.txt}}}
A-Z in the phonetic alphabet with the first letter capitalized, an empty line, then A-Z in the phonetic alphabet in all-uppercase.
\subsubsection*{\texttt{\textcolor{red}{sameline.txt}}}
The first four words in the phonetic alphabet on the same line, with Charlie and Delta having their last letter capitalized.
\subsubsection*{\texttt{\textcolor{red}{tailphonetic.txt}}}
The last 10 lines from phonetic.txt.
\subsubsection*{\texttt{\textcolor{red}{underscore.txt}}}
"\_Alpha", followed by an empty line, "Bravo\_", followed by an empty line, "Ch-arlie".
\subsubsection*{\texttt{\textcolor{red}{words.txt}}}
A copy of the words dictionary file.
\pagebreak
\section*{Automated Test Cases}
Automated tests may be executed with {\texttt{\color{red}make check}}, which builds and runs a bash script that performs unit tests for this program. Additional test details can be found in {\texttt{\color{red}test/test.bash}}; the script may have to be made executable before running.
\pagebreak
\section*{Common Test Cases}
Prerequisites: {\texttt{\color{red}intersect/}} directory does not already exist.
\subsection*{TC1: Installation}
\begin{enumerate}
  \item {\texttt{\color{red}git clone} {\color{blue}git@git.umbc.tc}}{\color{red}:tdqc/tdqc12/jviner/intersect.git}
  \item {\texttt{\color{red}cd intersect}}
\end{enumerate}
\textbf{Expected:} {\texttt{\color{red}intersect/}} directory is created.
\subsection*{TC2: Correct branch}
\begin{enumerate}
  \item {\color{red}git branch}
\end{enumerate}
\textbf{Expected:} {\color{red}main} is default branch.
\subsection*{TC3: Build cleaning}
\begin{enumerate}
  \item {\texttt{\color{red}make}}
  \item {\texttt{\color{red}make clean}}
  \item {\texttt{\color{red}ls}}
\end{enumerate}
\textbf{Expected:} No .o files or executable files are left in directory.
\pagebreak
\section*{Project-Building Test Cases}
Prerequisites: In the project's directory; have run {\texttt{\color{red}make clean}}.
\subsection*{TC4: Build Explicit}
\begin{enumerate}
  \item {\texttt{\color{red}make intersect}}
  \item {\texttt{\color{red}ls intersect}}
\end{enumerate}
\textbf{Expected:} File is listed.
\subsection*{TC5: Build Implicit}
\begin{enumerate}
  \item {\texttt{\color{red}make}}
  \item {\texttt{\color{red}ls intersect}}
\end{enumerate}
\textbf{Expected:} File is listed.
\subsection*{TC6: Build debugging}
\begin{enumerate}
  \item {\texttt{\color{red}make debug}}
  \item {\texttt{\color{red}readelf --debug-dump=decodedline intersect}}
\end{enumerate}
\textbf{Expected:} Debugging info is listed.
\subsection*{TC7: Build profiling}
\begin{enumerate}
  \item {\texttt{\color{red}make profile}}
\end{enumerate}
\textbf{Expected:} Program build output contains -gp flags.
\pagebreak
\section*{File-Based Test Cases}
Prerequisites: In the project's directory; have run {\texttt{\color{red}make}}; sample files in {\texttt{\color{red}samp/}} folder.
\subsection*{TC8: Leak Prevention - Very large files}
\begin{enumerate}
  \item {\texttt{\color{red}valgrind ./intersect samp/american-english.txt samp/words.txt > /dev/null}}
\end{enumerate}
\textbf{Expected:} Program does not enter infinite loop, exits normally, and valgrind shows no leaks.
\subsection*{TC9: Leak Prevention - Empty files}
\begin{enumerate}
  \item {\texttt{\color{red}valgrind ./intersect samp/empty.txt samp/empty.txt}}
\end{enumerate}
\textbf{Expected:} valgrind shows no leaks. Nothing is printed.
\subsection*{TC10: Leak Prevention - Nonexistent file}
\begin{enumerate}
  \item {\texttt{\color{red}valgrind ./intersect samp/empty.txt samp/nonexistentfile.txt}}
\end{enumerate}
\textbf{Expected:} valgrind shows no leaks. Appropriate error message printed.
\end{document}
